The Name of the Title is Hope

### 2023-12-13 input/2_introduction.tex

\section{Introduction}
% 1. Describe the Current Situtation
% Functions as a starting point and a common basis. Therefore it primarily contains recognizable and agreed points.
Advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities and simplifying skill acquisition~\citep{Goto2020-mw, Kunze2017-co}. However, augmented users often report dissociative experiences, frequently disrupting their sense of agency (SoA)~\citep{Gilbert2017-ze, Gilbert2019-uc}.

% 2. What is the complication, challenge identified
% Spells the reason for acting now. It contains threats / opportunities and the hurdles that need to be overcome.
Having a SoA means experiencing control of our own voluntary actions, instead of them feeling as randomly happening to us. It has frequently been shown that users are more likely to feel engaged and satisfied with an interaction, and are more likely to trust a system the more they experience SoA~\citep{Berberian2012-do, Miller2007-rb}. A key challenge to drive the adoption of human action augmentation then is to design for agency experience, so users feel as though they are in the ``driver's seat'' once again.

% 3. Question
% Asks the question how the hurdles of the Complication can be overcome. How can we prevent the threat or seize the opportunity? Also, what would be the benefits if the complication would be overcome?
% What have others done to address this and what do we propose "instead"
One goal of user augmentation is to increase reaction times, thereby making an interaction more efficient. Previous work on such augmentation scenarios has shown that an actuation preceding a movement by about 80 ms preserves agency~\cite{Kasahara2019-sk}. Evidence from cognitive neuroscience indicates that from around 200ms before a voluntary movement, users are unable to ``veto'' their self-initiated movement~\cite{Schultze-Kraft2016-bx}. Here, the \textit{key} aspect for SoA in action augmentation becomes apparent: External influences on the user's body need to be in line with the user's intention.

In experimental settings, this is typically achieved by using strongly controlled `stimulus-response' paradigms. For example, reaction times when tapping on a touchscreen in response to a presented stimulus on screen, can be reduced by an augmentation device while maintaining SoA for the user~\cite{Kasahara2019-sk, Kasahara2021-gy}. In such controlled scenarios, the timing of the action augmentation can be tuned to be near optimal because the user behavior can be predicted with very high certainty to follow a previously presented stimulus. However, a key challenge remaining is to design systems that maintain agency during unpredictable actions of the user and \textit{without} control over the environment. In other words, how can we design a closed-loop system to deliver a \textit{natural} agency experience for users' augmented actions?

@@

\subsection{Preserving Agency using Brain Signals of the Intent to (Inter-) act}
% 4. (long) Anwser with teaser image
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
In this paper, we present a bleeding edge prototype to challenge the disruption in experiencing agency during action augmentation. We developed a brain-computer interface (BCI) that establishes a fast communication channel between a user's brain signals and a physical end effector. The AUGMENTATION system (from hereon referred to simply as \textit{system}) controls the user's muscles at the time of their \textit{intent to interact}, as measured through readiness potentials (RP) manifesting in the user's electroencephalogram (EEG)~\cite{Nguyen2023-me, Schurger2021-vp, Schultze-Kraft2016-bx, Schultze-Kraft2021-cu}.

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/bci_game.png}
    \caption{Our AUGMENTATION system: When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's EEG signals. A brain-computer interface (BCI) predicts the data to be in either of two classes: Idle or pre-movement. In the latter case, the user's hand is moved by trigger electrical muscle stimulation (EMS). Image presented with consent from participant.}
\end{figure}

% TODO merge this with the figure below
% \missingfigure{maybe small infographic here showing the connection from EEG volitional RP thought to EMS trigger on the Arm. <- better use this for the teaser image. Here better present the main results, i.e. SoA scores? -> Klaus comment: yes, but they don't have to be exclusive. The general setup with the LRP could appear with the main results both in the teaser or here? But the teaser would be more a visualization of the principle, no? That does not necessarily require real results but could show a hyperplane and data dots for examplification.}
% make this as an infographic with comic style drawing of augmented user and then the three pathways drawn
% \begin{figure}
%     \centering
%     \includegraphics[width=\columnwidth]{figures/setup_conditions_draft_small.png}
%     \caption{draft apperatus and conditions}
%     \label{fig:setup}
% \end{figure}
% \begin{figure}[!h]
%     \centering
%     \includegraphics[width=\columnwidth]{figures/augmented_com_model_colour.png}
%     \caption{draft - visualization of comparator model of the SoA in the case of augmented interactions (inspired by Dewey 2019)}
%     \label{fig:com_model}
% \end{figure}

To control an interaction in real-time, the EEG-based RP classifier was used to discriminate between two user states: either the user was predicted to be in an \textit{idle} state, reflecting the absence of an intent to act-- or the user was predicted to be in a \textit{pre-movement} state, indicating the presence of an intent to act. When the system predicted a \textit{pre-movement} state, the user's action was augmented, potentially even before their own voluntary motor command. In our user study, we then applied a mixed-methods research approach to investigate whether keeping the physical impact on the user's body in line with their intention to move preserves their SoA.

%%% Resources
% add results and general outcomes here?

@@

>>>>

\section{Introduction}
% 1. Describe the Current Situtation
% Functions as a starting point and a common basis. Therefore it primarily contains recognizable and agreed points.
Advances in hardware that augment a user's physical actions have reignited dreams of overcoming human limitations, recovering lost abilities and simplifying skill acquisition~\citep{Goto2020-mw, Kunze2017-co}. \textcolor{green}{These technological advances include the miniaturization of the actuating hardware to wearable form factors and the direct sensing and stimulation capabilities of neural interfaces. Especially due to these characteristics, recent perspectives promote a change of the computing era from human-computer \textit{interaction} to \textit{integration}~\cite{Mueller2020-dl}. One key change in perspective is, that \textit{integrated} user's share agency with the computing machinery to execute tasks. This is a critical distinction as \textit{integration} technologies are designed to directly influence people’s bodies, their actions, and the resulting action outcomes.}

\textcolor{green}{Besides body and outcome augmentation, action augmentation has been defined as the case where a ``system assists the user’s action to produce the intended outcome.''~\cite{Cornelio2022-aq}. While such action augmentations can be realized purely on a software integration level, for example by an AI pair programmer, when it is designed to happen on a hardware level, further challenges emerge, specifically due to shared agency, which in this case means handing over control of ones body. Unfortunately,} such augmented users often report dissociative experiences, frequently disrupting their sense of agency (SoA)~\citep{Gilbert2017-ze, Gilbert2019-uc}.

% 2. What is the complication, challenge identified
% Spells the reason for acting now. It contains threats / opportunities and the hurdles that need to be overcome.
Having a SoA means experiencing control of our own voluntary actions, instead of them feeling as randomly happening to us. It has been shown that users are more likely to feel engaged and satisfied with an interaction, and are more likely to trust a system the more they experience SoA~\citep{Berberian2012-do, Miller2007-rb}. Hence, a key challenge to drive the adoption of human action augmentation then is to design for agency experience, so users feel as though they are in the ``driver's seat'' once again.

% 3. Question
% Asks the question how the hurdles of the Complication can be overcome. How can we prevent the threat or seize the opportunity? Also, what would be the benefits if the complication would be overcome?
% What have others done to address this and what do we propose "instead"
\textcolor{red}{One goal of green `on-body' action augmentation is to increase reaction times, thereby making an interaction more efficient. Previous work on such augmentation scenarios has shown that an actuation preceding a movement by about 80 ms preserves agency~\cite{Kasahara2019-sk}. Evidence from cognitive neuroscience indicates that from around 200ms before a voluntary movement, users are unable to ``veto'' their self-initiated movement~\cite{Schultze-Kraft2016-bx}. Here, the \textit{key} aspect for SoA in action augmentation becomes apparent: External influences on the user's body need to be in line with the user's intention.}

\textcolor{red}{In experimental settings, this is typically achieved by using strongly controlled `stimulus-response' paradigms. For example, reaction times when tapping on a touchscreen in response to a presented stimulus on screen, can be reduced by an augmentation device while maintaining SoA for the user~\cite{Kasahara2019-sk, Kasahara2021-gy}. In such controlled scenarios, the timing of the action augmentation can be tuned to be near optimal because the user behavior can be predicted with very high certainty to follow a previously presented stimulus. However, a key challenge remaining is to design systems that maintain agency during unpredictable actions of the user and \textit{without} control over the environment. In other words, how can we design a closed-loop system to deliver a \textit{natural} agency experience for users' augmented actions?}

@@

\subsection{Preserving Agency using Brain Signals of the Intent to (Inter-) act}
% 4. (long) Anwser with teaser image
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
In this paper, we present a prototype to overcome the disruption in experiencing agency during action augmentation. We developed a brain-computer interface (BCI) that establishes a fast communication channel between a user's brain signals and a physical end effector. The augmentation system (from hereon referred to simply as \textit{system}) controls the user's muscles at the time of their \textit{intent to interact}, as measured through readiness potentials (RP) manifesting in the user's electroencephalogram (EEG)~\cite{Schurger2021-vp, Schultze-Kraft2016-bx, Schultze-Kraft2021-cu}.

\begin{figure}[!h]
    \centering
    \includegraphics[width=\columnwidth]{figures/teaser_new.png}%{figures/bci_game.png}
    \caption{Our augmentation system: When participants feel the spontaneous urge to move, readiness potentials (RPs) are picked up in the user's brain signals. A brain-computer interface (BCI) predicts the data to be in either of two classes: Idle or pre-movement. In the latter case, electrical muscle stimulation (EMS) is triggered and the user's hand is moved. Image taken with consent from participant.}
\end{figure}

To control the interaction in real-time, an RP-based classifier distinguished between two user states: \textit{idle}, reflecting the absence of an intent to act, and \textit{pre-movement}, indicating the presence of an intent to act.\textcolor{red}{When the system predicted a \textit{pre-movement} state, the user's action was augmented, potentially even before their own voluntary motor command. In our user study, we then applied a mixed-methods research approach to investigate whether keeping the physical impact on the user's body in line with their intention to move preserves their SoA.} \textcolor{green}{During \textit{idle}, participants were passively looking at a fixation cross. Instead, during \textit{pre-movement}, participants were instructed to voluntarily initiate a tap on a touchscreen whenever they felt the urge to do so. Previous work has indicated that the RP emerges during formation of conscious intention and is specific to voluntary action~\cite{Schultze-Kraft2020-rm, Travers2020-hf, Pares-Pujolras2019-ll}.}

\textcolor{green}{Upon predicting a \textit{pre-movement} state, the system augmented the user's action, potentially preceding their voluntary motor command. This augmentation moved the ring finger in accordance with the user's intention to act. We achieved the movement by leveraging electrical muscle stimulation (EMS) applied to the user's forearm flexor muscle. In our user study, a mixed-methods research approach was employed to explore whether aligning the physical impact on the user's body with their intention to move preserved their Sense of Agency (SoA).}

%%% Resources
\begin{comment}
% TODO merge this with the figure below
% \missingfigure{maybe small infographic here showing the connection from EEG volitional RP thought to EMS trigger on the Arm. <- better use this for the teaser image. Here better present the main results, i.e. SoA scores? -> Klaus comment: yes, but they don't have to be exclusive. The general setup with the LRP could appear with the main results both in the teaser or here? But the teaser would be more a visualization of the principle, no? That does not necessarily require real results but could show a hyperplane and data dots for examplification.}
% make this as an infographic with comic style drawing of augmented user and then the three pathways drawn
% \begin{figure}
%     \centering
%     \includegraphics[width=\columnwidth]{figures/setup_conditions_draft_small.png}
%     \caption{draft apperatus and conditions}
%     \label{fig:setup}
% \end{figure}
% \begin{figure}[!h]
%     \centering
%     \includegraphics[width=\columnwidth]{figures/augmented_com_model_colour.png}
%     \caption{draft - visualization of comparator model of the SoA in the case of augmented interactions (inspired by Dewey 2019)}
%     \label{fig:com_model}
% \end{figure}

% add results and general outcomes here?

@@

\end{comment}

### 2023-12-13 input/3_related_work.tex

In the simple case of pressing a key on a piano, the finger movement is constantly compared to the predicted proprioceptive feedback. Subsequently, the tone generated by the key press is evaluated against auditory predictions. On a semantic level, these predictions may be in reference to whether the tone loudness corresponds to the velocity of the key press or whether the tone is in-key or out-of-key~\cite{Pangratz2023-ew}. If these predictions -- based on the intended movement and its expected outcome -- explain the sensory data available, agency is experienced.
% (see figure~\ref{fig:task_design} INTENTION).

In human-computer interaction (HCI) research, these constructs are categorized in their own terms. Often, the term \textit{pre-reflective} is used to describe `early', implicit, experience of agency, such as when matching proprioceptive predictions about finger movements. At higher levels of the cognitive hierarchy, \textit{reflective}, i.e. conscious, experience is used to refer to matching semantic predictions about action outcomes~\cite{Danry2022-xk, Cornelio2022-aq}.

As opposed to intended actions using our own body, movement augmentation hardware allows moving a user's body without their intention. Today, there are three main technologies to physically augment users' actions: Through the use of mechanical actuators, i.e. exoskeletons, a user's body can be moved by applying forces to the extremities. Another possibility is to stimulate the brain directly, so the stimulation causes a motor response, for example by using transcranial magnetic stimulation (TMS). Lastly, electrical muscle stimulation (EMS) makes the user's extremities move by sending current into their muscle-activating nerves. In these scenarios, the user computes no predictions about the movement and its outcome. Thus, in reference to the comparator model, none or a decreased SoA arises in the case of externally controlled actions, for example by brain stimulation~\cite{Haggard2002-sz} or when the body is moved by another person~\cite{Kuhn2013-ls}. With something or somebody else moving our body to perform, e.g., a key press on a piano, the lack of intention to play the piano -- and derived sensory and semantic predictions -- impacts the experience of agency. Such involuntary movements may even cause adverse effects: In case a body movement is elicited by TMS simulation, a resistance to the movement may manifest~\cite{Haggard2002-sz}.
% (see figure~\ref{fig:task_design} EXTERNAL CONTROL)

@@

On the other hand, implicit methods are often used to query low-level pre-reflective sensory predictions that are not consciously reflected~\cite{Moore2016-ub, Limerick2014-un, Moore2012-ic}. Following seminal work in neuroscience has described one effect of SoA as a bias in the perception of action \textit{outcome}: Intentional binding paradigms state that when a button press is followed by a -- delayed -- outcome, participants mentally compress the delay~\cite{Haggard2002-sz}. Critically, this temporal compression only occurs following movement intention. The action outcome is mentally \textit{bound} to the intention. To reduce uncertainty about the binding, the brain `explains away' the excess delta, compressing the action-outcome delay~\cite{Barlas2018-bq}. Supplementing this behavioral phenomenon, physiological evidence can prove useful to further understand the interplay between volitional action and the SoA.

% alternative subsection heading: Brain Signals Reflecting the Intent to (Inter-)Act
% this must make the link clear that we need intention for agency experience and intention is something we can set out to measure using EEG!!!
\subsection{Controlling Actuated Haptic Experiences using Brain Signals Reflecting the Intent to (Inter-)act}
Of the possible physiological signals that can be used to further investigate the experience of agency, the electroencephalogram (EEG) is very well suited because of its high temporal resolution and the non-invasive recording close to the motor command generating structures in the human brain. The Readiness Potential (RP), or \textit{lateralized readiness potential} is an amplitude fluctuation in the ongoing EEG activity that has frequently been observed preceding voluntary action~\cite{Deecke1969-bl, Libet1983-qu}. The RP is reliably observed at electrodes placed over the motor cortex contralateral to the acting hand. Since its measurable onset precedes the time of participants' self-reported conscious movement intention, it has drawn much interest with respect to the debate on free will, see~\cite{Schurger2021-vp} for a recent neuroscientific perspective. However, evidence abounds for its role in action preparation. An RP is typically comprised of two stages: an early slow stage that begins up to two seconds before the actual movement and a late steep stage that starts about 400 milliseconds before movement. The first stage manifests in the pre-supplementary motor area and transfers to the premotor cortex shortly after. The second stage manifests contra-laterally in the primary motor cortex~\cite{Shibasaki2006-mt}.

A recent study has shown that the RP is ingrained in the subconscious mechanisms preceding movements that people cannot explicitly suppress~\cite{Schultze-Kraft2021-cu}. In their study,~\citet{Schultze-Kraft2021-cu} asked participants to find a way to perform voluntary movements while keeping accompanying RP amplitudes as small as possible. After each trial they informed participants about the strength of the RP in the current trial, so participants had a feedback metric to optimize for. They found participants unable to suppress their RP. This inability to suppress the RP renders it a reliable feature for classification. For example, the RP can be detected in real-time using a brain-computer interface (BCI).~\citet{Schultze-Kraft2016-bx} demonstrated a prototype that detects RPs in participants ongoing EEG data and adapts an interface accordingly. Participants were instructed to veto their self-initiated movement whenever a red dot occurred on the screen. The red dot's appearance was controlled by the BCI. Whenever an RP was detected, the red dot appeared. The authors found that participants were able to veto their self-initiated movement if the red dot appeared no later than 200ms preceding their movement onset. After that, participants were unable to ``overwrite'' their motor command and acted regardless of the red dot appearance on screen.

In the present study, we leveraged the RP in a similar way, i.e. to discriminate between two \textit{action} states as the basis to trigger an action augmentation device or not. The technology we used with our system, electrical muscle stimulation (EMS), sends currents to the user's forearm leading to a contraction of the flexor muscle moving the ring finger as an augmented movement.

%%% resources

\begin{comment}

@@

%%%%%%%%%%%%%%%%%%%%%%
Other
- EEG patterns related to readiness potential and intentional  binding sometimes show disceprant patterns ( see WEN and Imamizu 38 und 39) (wittmann 2014, Goldberg 2017)
\end{comment}

>>>>

In the simple case of pressing a key on a piano, the finger movement is constantly compared to the predicted proprioceptive feedback. Subsequently, the tone generated by the key press is evaluated against auditory predictions. On a semantic level, these predictions may be in reference to whether the tone loudness corresponds to the velocity of the key press or whether the tone is in-key or out-of-key~\cite{Pangratz2023-ew}. If these predictions -- based on the intended movement and its expected outcome -- explain the sensory data available, agency is experienced.
%, see figure~\ref{fig:task_design} INTENTION).

In human-computer interaction (HCI) research, these constructs are categorized using a different terminology. Often, the term \textit{pre-reflective} is used to describe `early', implicit, experience of agency, such as when matching proprioceptive predictions about finger movements. At higher levels of the cognitive hierarchy, \textit{reflective}, i.e. conscious, experience is used to refer to matching semantic predictions about action outcomes~\cite{Danry2022-xk, Cornelio2022-aq}.

As opposed to intended actions using our own body, movement augmentation hardware allows moving a user's body without their intention. Today, there are three main technologies to physically augment users' actions: Through the use of mechanical actuators, i.e. exoskeletons, a user's body can be moved by applying forces to the extremities. Another possibility is to stimulate the brain directly, so the stimulation causes a motor response, for example by using transcranial magnetic stimulation (TMS). Lastly, electrical muscle stimulation (EMS) makes the user's extremities move by sending current into their muscle-activating nerves. In these scenarios, the user computes no predictions about the movement and its outcome. Thus, concerning the comparator model, none or a decreased SoA arises in the case of externally controlled actions, for example by brain stimulation~\cite{Haggard2002-sz} or when the body is moved by another person~\cite{Kuhn2013-ls}. With something or somebody else moving our body to perform, e.g., a key press on a piano, the lack of intention to play the piano -- and derived sensory and semantic predictions -- impacts the experience of agency. ~\textcolor{red}{Such involuntary movements may even cause adverse effects: In case a body movement is elicited by TMS simulation, a resistance to the movement may manifest~\cite{Haggard2002-sz}.}
%, see figure~\ref{fig:task_design} EXTERNAL CONTROL)}

@@

On the other hand, implicit methods are often used to query low-level pre-reflective sensory predictions that are not consciously perceived~\cite{Moore2016-ub, Limerick2014-un, Moore2012-ic}. Seminal work in neuroscience has described one effect of SoA as a bias in the perception of action \textit{outcome}: Intentional binding paradigms state that when a button press is followed by a -- delayed -- outcome, participants mentally compress the delay~\cite{Haggard2002-sz}. Critically, this temporal compression only occurs following movements that were intended. The action outcome is mentally \textit{bound} to the intention. To reduce uncertainty about the binding, the brain `explains away' the excess delta, compressing the action-outcome delay~\cite{Barlas2018-bq}. Supplementing this behavioral phenomenon, physiological evidence can prove useful to further understand the interplay between volitional action and the SoA.

\subsection{\textcolor{green}{Controlling Actuated Haptic Experiences}}

\textcolor{green}{Experimental setups to investigate new `on-body' augmentation technologies that aim to preserve the user's SoA frequently use highly controlled `stimulus-response' paradigms. For example, scenarios where participants are instructed to tap on a touchscreen in response to a presented stimulus on the screen. Here, participants' behavior can be predicted with very high certainty to follow the presented stimulus, and estimating their reaction time is very accurate. In such controlled scenarios, the timing of an action augmentation device can be tuned to be near optimal. Hence, \textit{pre-empting} the user's motion can be designed to fall in line with their intention to move, thereby maintaining SoA. Previous work on such an augmentation scenario has shown that an actuation preceding a movement by about 80 ms preserves agency~\cite{Kasahara2019-sk, Kasahara2021-gy}.}

\textcolor{green}{Evidence from cognitive neuroscience indicates that from around 200ms before a voluntary movement, users are unable to ``veto'' their self-initiated movement~\cite{Schultze-Kraft2016-bx}. Here, the \textit{key} aspect for SoA in action augmentation becomes apparent: External influences on the user's body need to be in line with the user's intention. However, a key challenge remaining is to design systems that maintain agency during unpredictable actions of the user and \textit{without} control over the environment. In other words, how can a closed-loop system to deliver a \textit{natural} agency experience for users' augmented actions be designed?}

\textcolor{red}{\subsection{Controlling Actuated Haptic Experiences using Brain Signals Reflecting the Intent to (Inter-)act}}

\subsubsection{\textcolor{green}{Using Brain Signals Reflecting the Intent to (Inter-)act for Action Augmentation}}
\textcolor{green}{One possible design solution is to leverage physiological signals for action augmentation}. Of the possible physiological signals that can be leveraged\textcolor{red}{used to further investigate the experience of agency}, the EEG is very well suited because of its high temporal resolution and the non-invasive recording close to the motor command generating structures in the human brain. The RP, or \textit{lateralized readiness potential}, is an amplitude fluctuation in the ongoing EEG activity that has frequently been observed preceding voluntary action~\cite{Deecke1969-bl, Libet1983-qu}. The RP is reliably observed at electrodes placed over the \textcolor{green}{sensori}motor cortex contralateral to the acting hand.~\textcolor{green}{In the 10-20 system for EEG electrode placement~\cite{Jasper1983-uw}, these are electrode C3 located over the sensorimotor cortex of the left hemisphere, and C4 vice versa. However, activity observed at electrode Cz is reported most frequently as it reflects neural activity originating from the sensorimotor cortex without lateralization bias.} Since the RPs' measurable onset precedes the time of participants' self-reported conscious movement intention, it has drawn much interest with respect to the debate on free will, see~\cite{Schurger2021-vp} for a recent neuroscientific perspective. However, evidence abounds for its role in action preparation. An RP is typically comprised of two stages: an early slow stage that begins up to two seconds before the actual movement and a late steep stage that starts about 400 milliseconds before movement. The first stage manifests in the pre-supplementary motor area and transfers to the premotor cortex shortly after. The second stage manifests contra-laterally in the primary motor cortex~\cite{Shibasaki2006-mt}.

A recent study has shown that the RP is ingrained in the subconscious mechanisms preceding movements that people cannot explicitly suppress~\cite{Schultze-Kraft2021-cu}. In their study,~\citet{Schultze-Kraft2021-cu} asked participants to find a way to perform voluntary movements while keeping accompanying RP amplitudes as small as possible. After each trial they informed participants about the strength of the RP in the current trial, so participants had a feedback metric to optimize for. They found participants unable to suppress their RP. This inability to suppress the RP renders it a reliable feature for classification. For example, the RP can be detected in real-time using a brain-computer interface (BCI).~\citet{Schultze-Kraft2016-bx} demonstrated a prototype that detects RPs in participants ongoing EEG data and adapts an interface accordingly. Participants were instructed to veto their self-initiated movement whenever a red dot occurred on the screen. The red dot's appearance was controlled by the BCI. Whenever an RP was detected, the red dot appeared. The authors found that participants were able to veto their self-initiated movement if the red dot appeared no later than 200ms preceding their movement onset. After that, participants were unable to ``overwrite'' their motor command and acted regardless of the red dot's appearance on screen.

\textcolor{red}{In the present study, we leveraged the RP in a similar way, i.e. to discriminate between two \textit{action} states as the basis to trigger an action augmentation device or not. The technology we used with our system, electrical muscle stimulation (EMS), sends currents to the user's forearm leading to a contraction of the flexor muscle moving the ring finger as an augmented movement.}

%%% resources
\begin{comment}

@@

%%%%%%%%%%%%%%%%%%%%%%
Other
- EEG patterns related to readiness potential and intentional  binding sometimes show disceprant patterns ( see WEN and Imamizu 38 und 39) (wittmann 2014, Goldberg 2017)
